Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-23 paper.tex
More content for section 4.1 (compatibility)

Examples worth mentioning in this context is eyeOS (2005)~\cite{liu2012research}~\cite{vidyabanu2011implementation}, which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. Despite being open source, it has never become widely used since it is impossible to import and use native Windows or Linux applications with this software. All required applications have to be developed as web applications. This limitation especially caused most potential users to lose interest in web desktops because many popular native applications can hardly be replaced or re-developed, and many feature-rich and well-established Software-as-a-Service offerings like Microsoft Office 365 and Google Docs already exist.

The development of DaaS solutions in the past shows that a new DaaS will only be accepted by a broad user group if it enables the integration of native applications in an unchanged manner. It is also desirable that a DaaS supports applications for the Linux and Windows operating systems to enable flexible working and make the operation of a virtualization solution on the desktops unnecessary. Ideally, it should also be possible to run native MacOS applications. However, this goal is difficult to achieve under legal conditions due to the licensing restrictions of the MacOS operating system.

Sound (via sound-deamon oder via Guacamole)

Drucker (via cups oder via Guacamole)

Externe Geräte (USB-Stick)

>>>>

Examples worth mentioning in this context are eyeOS and SilveOS. The project eyeOS~\cite{liu2012research}~\cite{vidyabanu2011implementation} which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. The project SilveOS~\cite{garmpis2016design} mimics the look and feel of Windows 10 in the browser using the discontinued application framework Microsoft Silverlight. Despite being open source, both solutions have never become widely used since it is impossible to import and use native Windows or Linux applications with such solutions. All required applications have to be developed as web applications. This limitation especially caused most potential users to lose interest in web desktops because many popular native applications can hardly be replaced or re-developed, and many feature-rich and well-established Software-as-a-Service offerings like Microsoft Office 365 and Google Docs already exist.

The development of DaaS solutions in the past shows that a new DaaS will only be accepted by a broad user group if it enables the integration of native applications in an unchanged manner. It is also desirable that a DaaS supports applications for the Linux and Windows operating systems to enable flexible working and make the operation of a virtualization solution on the desktops unnecessary. Ideally, it should also be possible to run native Mac OS applications. However, this goal is difficult to achieve under legal conditions due to the Mac OS operating system's licensing restrictions.

Further essential features for most users are printing, sound, and compatibility with external storage media.

% !!!!!!
% Vermutlich ist das einfach gar nicht relevant hier... wenn doch, müssen wir es sinnvoll einbauen.
% !!!!!!
% On Linux operating systems, sound and microphone devices are accessed via sound servers like PulseAudio and PipeWire, which interact with the sound interface present in the kernel, e.g., Advanced Linux Sound Architecture (ALSA) or Open Sound System (OSS). ...

Guacamole supports redirecting audio, printing, and disk access via the protocol RDP. The printing feature does not allow access to local or remote printers; instead, it allows users to print directly to PDF files, which are received by the user's web browser. As a prerequisite, the GhostScript interpreter must be deployed on the Guacamole server.
File transfer over RDP supports Guacamole by emulating a virtual disk drive that persistently stores data on the Guacamole server.~\cite{ApacheGuacamole2024}

Compared to RDP, the protocol VNC offers fewer features in Guacamole since it does not support sound on its own. However, Guacamole supports sound using PulseAudio as a workaround solution. VNC also does not offer file transfer and access to external storage media, but as a workaround solution, Guacamole supports file transfer file transfer over SSH using the protocol SFTP.
